Paper Visualizations

### 2022-05-24 eda/paper-graphics.Rmd
out file for table1
table3

#create table
stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l')
```

@@

stargazer(forg_privacy, forg_privacy_interactions, forg_undue, forg_undue_interactions, lif_undue, lif_undue_interactions, relauo_undue, relauo_undue_interactions,
          title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5", "Model 6", 
                            "Model 7", "Model 8"))
# , covariate.labels = c("Justice Ideology", "Justice Gender", "Lower Court Decision", "Solicitor General Amicus Brief", "pfemam", "forgauf_privacy", "justicemq:forgauf_privacy", "forgauf_undue_burden", "justicemq:forgauf_undue_burden", "poppam", "lifauo_undue_burden", "justicemq:lifauo_undue_burden"))
```

@@

stargazer(forg_womenhealth, forg_womenhealth_interactions, medauf_womenhealth, medauf_womenhealth_interactions, forg_womenfuture, relauo_abortionregret, forg_evidence, forg_evidence_interactions, medauo_evidence, medauo_evidence_interactions
          ,title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5", "Model 6", 
                            "Model 7", "Model 8", "Model 9", "Model 10"))
```

@@

stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality
          ,title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5"))
```

>>>>

#create table
stargazer(author_table, summary=FALSE, rownames=FALSE, title = "Table 1.  Total Number of Amicus Briefs by Amicus Type in the Supreme Court Abortion Cases", notes = "a. Legal cases can have more than one amicus type filed in a case (e.g., differing groups of feminist organizations can file more than one brief in a case).  Also, the same organizations file briefs in multiple cases.", header=FALSE, type = 'html', notes.align = 'l', out = "graphics/table1.htm")
```

@@

stargazer(forg_privacy, forg_privacy_interactions,
          forg_undue, forg_undue_interactions,
          lif_undue, lif_undue_interactions,
          relauo_undue, relauo_undue_interactions,
          type='html',align=TRUE,
          model.numbers = F, ci=T,
          dep.var.labels="Justice Vote (1 = Fem)",
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5", "Model 6", 
                            "Model 7", "Model 8"),
          order=c("forgauf_privacy", "justicemq:forgauf_privacy",
                  "forgauf_undue_burden", "justicemq:forgauf_undue_burden",
                  "lifauo_undue_burden", "justicemq:lifauo_undue_burden",
                  "relauo_undue_burden", "justicemq:relauo_undue_burden",
                  "justicemq","justicefem","pfemam","poppam","sgfem3","lcdisdirfem"),
          covariate.labels = c("feminist org privacy","feminist org privacy X justice ideology",
                               "feminist org undue burden", "feminist org undue burden x justice ideology",
                               "prolife org undue burden", "prolife org undue burden x justice ideology",
                               "religious (AA) undue burden", "religious (AA) undue burden X justice ideology",
                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
                               "SG amicus brief", "lower court decision"),
          out="graphics/table2.htm")
```

@@

stargazer(forg_womenhealth, forg_womenhealth_interactions, 
          medauf_womenhealth, medauf_womenhealth_interactions,
          forg_womenfuture,
          relauo_abortionregret,
          forg_evidence, forg_evidence_interactions,
          medauo_evidence, medauo_evidence_interactions,
          title="Results", type='html',align=TRUE,
          model.numbers = F, ci=T,
          dep.var.labels="Justice Vote (1 = Fem)",
          column.labels = c("Model 1", "Model 2", 
                            "Model 3", "Model 4", "Model 5", "Model 6", 
                            "Model 7", "Model 8", "Model 9", "Model 10"),
          order=c("forgauf_womens_health", "justicemq:forgauf_womens_health",
                  "medauf_womens_health", "justicemq:medauf_womens_health",
                  "forgauf_womens_future_life",
                  "relauo_abortion_regret",
                  "forgauf_evidence", "justicemq:forgauf_evidence",
                  "medauo_evidence", "justicemq:medauo_evidence",
                  "justicemq","justicefem","pfemam","poppam","sgfem3","lcdisdirfem"),
          covariate.labels = c("feminist org women's health", "feminist org women's health X justice ideology",
                               "medical (RR) women's health", "medical (RR) women's health x justice ideology",
                               "feminist org women's futures",
                               "religious (AA) abortion regret", 
                               "feminist org expert evidence", "feminist org expert evidence X justice ideology",
                               "medical (RR) expert evidence", "medical (RR) expert evidence X justice ideology",
                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
                               "SG amicus brief", "lower court decision"),
          out="graphics/table3.htm")
```

@@

stargazer(forg_fetus, forg_morality, relauo_fetus, relauo_fetus_interactions, medauo_morality,
          title="Results", type='html',align=TRUE,
          column.labels = c("Model 1", "Model 2", "Model 3", "Model 4", "Model 5"),
          model.numbers = F, ci=T,
          dep.var.labels="Justice Vote (1 = Fem)",
          order=c("forgauf_fetus",
                  "forgauf_morality_religion",
                  "relauo_fetus", "justicemq:relauo_fetus",
                  "medauo_morality_religion",
                  "justicemq","justicefem1","pfemam","poppam","sgfem3","lcdisdirfem1"),
          covariate.labels = c("feminist org fetus",
                               "feminist org morality and religious",
                               "religious (AA) fetus", "religious (AA) fetus X justice ideology",
                               "medical (RR) morality",
                               "justice ideology", "justice gender", "proportion RR", "proportion AA",
                               "SG amicus brief", "lower court decision"),
          out="graphics/table4.htm")
```
